A Survey on Ordered Binary Decision Diagrams

### 2015-09-15 paper.tex
Add EfUg description

$\text{\textbf{EX}} f$ is satisfied for a state $s$ iff a state satisfying $f$
exists and $R \left( s, t \right)$ holds. In terms of $\mu$-Calculus relational
terms, $\text{\textbf{EX}} f$ can be formulated as
$\lambda u \lbrack \exists v \left( f(v) \land R \left( u, v \right) \right) \rbrack$.

\tbr

>>>>

$\text{\textbf{EX}} f$ is satisfied for a state $s$ iff a state satisfying $f$
exists and $R \left( s, t \right)$ holds. In terms of $\mu$-Calculus relational
terms, $\text{\textbf{EX}} f$ can be formulated as
$\lambda u \lbrack \exists v \left( f(v) \land R \left( u, v \right) \right) \rbrack$~\cite{BURCH90}.

The other two formulas are represented by fixed point characterizations, computed
using direct iteration or iterative squaring (see~\cite[p. 433]{BURCH90}).

$\text{\textbf{E}} \lbrack f_1 \text{\textbf{U}} f_2 \rbrack$ is satisfied for a
state $s$ if $f_2$ is satisfied by $s$ or $s$ satisfies $f_1$ and $s$ has a
successor state $t$ such that a path exists starting at $t$ and satisfying
$f_1 \text{\textbf{U}} f_2$. The $\mu$-Calculus representation is defined by
$\mu Q \lbrack f_2 \lor \left( f_1 \land \text{\textbf{EX}} Q \right) \rbrack$~\cite{BURCH90}.\tbr
